Insert Title

### 2017-01-23 paper/main.tex
Update to the paper

\begin{figure}
\begin{center}
\begin{tabular}{c c}
\includegraphics[scale=0.25]{Images/5By5One.png} &
\includegraphics[scale=0.25]{Images/5By5Two.png}
\end{tabular}
\end{center}
\caption{These images represent traffic flow from 5 tollbooths into 5 highway lanes. The image on the right is one time step after the image on the left. The cars begin at the top and move towards the bottom.}
\label{fig:5By5}
\end{figure}
% Need to explain the visualization.

@@

Before considering statistics and such, consider Figure \ref{fig:5By5}. This is a visualization of our model, it shows the structure of the world space which the cars live in. As you can see here, the cars in this simulation live somewhere with no lanes ended. Other figures you will be able to see the shape of where the cars live, as well as approximately the density.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.2]{Images/55_ez.png}
\caption{Travel times for L = 5, B = 5 baseline case for automated tollbooths. Mean is 23.4 seconds. }
\label{fig:ez55}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.2]{Images/55_man.png}
\caption{Travel times for the L = 5, B = 5 baseline case for manual tollbooths. Mean is 22.5 seconds.}
\label{fig:manual55}
\end{center}
\end{figure}

@@

A weakness of our model is the autonomous cars. Although they exhibit the behaviors of autonomous vehicles (rule following, speed matching, others), they do not distinguish themselves a sufficient amount from the `human' driven cars. This is a difficult problem for a micro-simulation or multi-agent system model, as both the human driven cars and the self-driven cars are at their core simulated by code. Therefore making a meaningful distinction is difficult. The behavior of the cars does 
%
%
%
%
%
Cost is a potential weakness in our final design. Since the structure takes up a greater area than traditional merge zones, this design could cost more to build. However, we believe that the open space could be put to a purpose that could lead to a more profitable toll area, offsetting the additional costs.

\subsection{Final Recommendation}
\label{final_rec}

>>>>

\begin{figure}[H]
\begin{center}
\begin{tabular}{c c}
\includegraphics[scale=0.2]{Images/5By5One.png} &
\includegraphics[scale=0.2]{Images/5By5Two.png}
\end{tabular}
\end{center}
\caption{These images represent traffic flow from 5 tollbooths into 5 highway lanes. The image on the right is one time step after the image on the left. The cars begin at the top and move towards the bottom.}
\label{fig:5By5}
\end{figure}
% Need to explain the visualization.

@@

Before considering statistics, consider Figure \ref{fig:5By5}. This is a visualization of our model and shows the structure of the world space which the cars live in. As you can see here, the cars in this simulation live somewhere with no lanes ended. Other figures you will be able to see the shape of where the cars live, as well as approximately the density.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.15]{Images/55_ez.png}
\caption{Travel times for L = 5, B = 5 baseline case for automated tollbooths. Mean is 23.4 seconds. }
\label{fig:ez55}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.15]{Images/55_man.png}
\caption{Travel times for the L = 5, B = 5 baseline case for manual tollbooths. Mean is 22.5 seconds.}
\label{fig:manual55}
\end{center}
\end{figure}

@@

A weakness of our model is the autonomous cars. Although they exhibit the behaviors of autonomous vehicles (rule following, speed matching, others), they do not distinguish themselves a sufficient amount from the `human' driven cars. This is a difficult problem for a micro-simulation or multi-agent system model, as both the human driven cars and the self-driven cars are at their core simulated by code. Therefore making a meaningful distinction is difficult. The behavior of the cars does stand out, but not perhaps to the degree that is desirable. 
%
%
%
%
%
Cost is a potential weakness in our final design. Since the structure takes up a greater area than traditional merge zones, this design could cost more to build. However, we believe that the open space could be put to a purpose that could lead to a more profitable toll area, offsetting the additional costs.

Finally, we were unable to definitively determine the reason that cars were able to travel faster in structures where B=L than in structures where B $<$L. This was counter to what we expected, but we suspect the reason is that each of our road designs would have a different capacity, or critical density. This would change the relationship between throughput and travel time. Given more time, we would have liked to identi 
\subsection{Final Recommendation}
\label{final_rec}
